% !TeX root = ../HistoryIA.tex

This investigation has brought to my attention several key features of the methods used by historians. I have found that the foremost challenge I faced in this,
and which is central to the process of studying and writing of history, was an understanding of which sources, lenses, and conclusions were appropriate to consider
in the course of my research. For instance, the economic analysis of Britain's neutrality during the American Civil War, a lens which I initially considered to
be at the core of this investigation, is one which, for various reasons, is not accepted by the historiography on the subject. As such, I had to reconsider the
conclusions which I had expected to draw from my research, and which seemed to me almost self-evident from a precursory glance, and approach the question from
a more subtle and nuanced lens. This did, in the end, lead me to a much more satisfying conclusion, however it was not one which was easy to arrive at.

Further, and as I touched upon in my mention of Owsley's \textit{King Cotton Diplomacy}, the nature of academic discourse during early-to-mid 20th
century has led me to conduct a critical evaluation of each source I made reference to, insofar as to check for content containing a significant bias towards
the Confederacy. My reliance on scholarly works has been heavy, and, though many of the most commonly-cited works on the topic were written during the period
mentioned, I have made deliberate efforts to use more recent studies to fill in the gaps left by the older ones. 

I have, to the best of my ability, answered the question posed, through a lens which is accepted in the current historiographical zeitgeist on the topic. The
lens of analysis I have used is not suitable for a complete understanding of the issue, a fact that has become increasingly clear to me as I have researched this
topic. This is, I believe, the largest challenge of the historian, and one which is endemic to the nature of historical events as multifaceted and complex
events: no single study, regardless of its breadth and/or depth, shall ever be able to fully capture an event and its many interpretations.